\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Captioned figure & stuff

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{B(t).png}
  \caption{An example of a zone's population density as a function of travel time from another zone.}
  \label{fig:sub1}
\end{subfigure}%
\hfill
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{A(t)B(t).png}
  \caption{TODO(drew)}
  \label{fig:sub2}
\end{subfigure}
\caption{Overarching caption whatever}
\label{fig:test}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{6point.pdf}
\caption{TODO(drew)}
\label{A(t)B(t)}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{greedy6point.pdf}
\caption{TODO(drew)}
\label{A(t)B(t)}
\end{center}
\end{figure}

@@

\subsubsection{$n=3$}
We ran the greedy algorithm for $n=3$ and we got that ambulances should be placed in zones
2, 3, and 5. This arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of
zone 1.

>>>>

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{B(t).png}
  \caption{An example of a zone's population density as a function of travel time from another zone.}
  \label{fig:sub1}
\end{subfigure}%
\hfill
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{A(t)B(t).png}
  \caption{TODO(drew)}
  \label{fig:sub2}
\end{subfigure}
\label{fig:test}
\end{figure}

@@

@@

\subsubsection{$n=3$}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{6point.pdf}
\caption{Graph of zones, populations, and travel times}
\end{center}
\label{fig:fullgraph}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{greedy6point.pdf}
\caption{Graph as in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
\end{center}
\end{figure}

We ran the greedy algorithm for $n=3$ and we got that ambulances should be placed in zones
2, 3, and 5. This arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of
zone 1.
